Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-12-02 R/model_fcs_check.Rmd
Update model_fcs_check.Rmd

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer^* <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 12,
  fig.height = 12,
  dpi = 600
  )
```

>>>>

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "Markus Bauer^* <br>"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  github_document:
    toc: true
    toc_depth: 2
    dev: jpeg
    fig_width: 12
    fig_height: 12
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE
  )
```
